Designing and Developing a Personalised Recommender System

### 2021-01-29 paper/paper.tex
filtered business file to restaurants only

\subsection{Data description}
The data I am using is taken from the Yelp dataset,
it includes user reviews of different businesses and services in a specific location.
These user reviews include ratings, text feedback, and other such information.

\subsection{Data preparation and feature selection}
Prepare data
The entire Yelp dataset is huge and much of it is not neccessary for my domain of bars.
As such I prepared the data by eliminating any data not relevant to my domain.
I selected features such as user ratings and a particular user's average rating,
since if a user typically rates places they go highly, but rates a particular bar low,
this is more significant than a user who always rates places low.

@@

\subsection{Further developments}
What could I do in the future

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}

>>>>

\subsection{Data description}
The data I am using is taken from the Yelp dataset,
it includes user reviews of different businesses and services in a specific location.
There are 10 cities included in the dataset: Montreal, Calgary, Toronto, Pittsburgh, Charlotte, 
Urbana-Champaign, Phoenix, Las Vegas, Madison, and Cleveland. 
These user reviews include ratings, text feedback, and other such information.

\subsection{Data preparation and feature selection}
Prepare data
Of the 209,393 businesses in the dataset, 168,903 are still open.
The entire Yelp dataset is huge and much of it is not necessary for my domain of bars.
As such I prepared the data by eliminating any data not relevant to my domain.
I selected features such as user ratings and a particular user's average rating,
since if a user typically rates places they go highly, but rates a particular bar low,
this is more significant than a user who always rates places low.

@@

\subsection{Further developments}
What could I do in the future \cite{5284958}.

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,references}
